---
title: "Appendix"
output:
  word_document: default
  pdf_document: default
---

### Power analysis

The following code was used to run a power analysis based on the meta-analytic mean.

First, we need to clear up the memory and load the necessary library.

```{r}
# clear memory
rm(list=ls())

# package needed
library(pwr)
```

Furthermore, we create a function to transform Zr values to r values. This is because
our meta-analysis was based on Zr values, but what the power analysis is based on r values.

```{r}
# function to convert Zr to r        
Zr.to.r<-function(Zr){
  r<-(exp(2*Zr)-1)/(exp(2*Zr)+1)
}
```

### Power analysis

Next, we estimated the sample size necessary to find a effect size as small as the one 
estimated by our meta-analysis (Zr = 0.20). We used a significance level of 0.05, and the 
recommended 80% statistical power(Cohen 1988).

```{r}
pwr.r.test(r = Zr.to.r(0.20), sig.level = 0.05, power = 0.8)
```

### Power analysis

This shows that we would need the dominance rank and bib size of 198 individuals to find 
a signicant correlation of 0.20. 

Additionally, we estimated the across-study statistical power of the tests on
status signalling in house sparrows to compare it the overall statistical power
found in the literature (Jennions and Moller 2003).

```{r}
pwr.r.test(n = 10, r = Zr.to.r(0.20), sig.level = 0.05)
```

### Power analysis

This shows that the statistical power of the sparrow literature on status signalling is
as low as 8.5%, which is alarming.